---
title: "R_Badge"
output: html_document
date: "2024-06-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=F}
# load libraries

library(tidyverse)
```


## Project Euler Code 

### Task 1:

```{r}
multiple3 <- seq(3,999,3)
multiple5 <- seq(5,999,5)

q1 <- sum(multiple3) + sum(multiple5)
q1
```

### Task 2:

```{r}
a <- 1
b <- 2
sum <- 0

while (b<=4000000){
  if (b%%2==0){
    sum <- sum+b
  }
  
  next_num <- a+b
  a <- b
  b <- next_num
}

print(sum)
```

### Task 3:

```{r}
prime_factors <- function(n){
  largest<- 1

  while(n%%2==0){
    largest<-2
    n <- n / 2
    }

  odd_factors <- 3
  max_factor <- sqrt(n)
  while(odd_factors <= max_factor){
    while (n %% odd_factors == 0) {
      largest <- odd_factors
      n <- n / odd_factors
      max_factor <- sqrt(n)
    }
    odd_factors <- odd_factors + 2
    }
if (n > 2) {
    largest <- n
}
return(largest)
}

prime_factors(600851475143)
```
## Distribution Histograms

### Uniform
```{r}
udata <- runif(10)
u_df <- data.frame(udata = udata)

ggplot(u_df, aes(x=udata)) +
  geom_histogram(fill="Magenta", color="black", bins=7) +
  labs(x="Value", y="Frequency", title="Histogram of Uniform Distribution Frequencies") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

### Poisson

```{r}
pdata <- rpois(10, 5)
p_df <- data.frame(pdata = pdata)

ggplot(u_df, aes(x=pdata)) +
  geom_histogram(fill="Chartreuse3", color="black", bins=7) +
  labs(x="Value", y="Frequency", title="Histogram of Poisson Distribution Frequencies") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

### Normal

```{r}
rdata <- rnorm(10)
r_df <- data.frame(rdata = rdata)

ggplot(r_df, aes(x=rdata)) +
  geom_histogram(fill="skyblue", color="black", bins=9) +
  labs(x="Value", y="Frequency", title="Histogram of Normal Distribution Frequencies") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

```

## Binomial and Normal Convergence

```{r}
# binomial distribution

rdata1 <- rbinom(10, 10, 0.5)
rdf1 <- data.frame(rdata1 = rdata1)

rdata2 <- rbinom(100, 10, 0.5)
rdf2 <- data.frame(rdata2 = rdata2)

rdata3 <- rbinom(1000, 10, 0.5)
rdf3 <- data.frame(rdata3 = rdata3)

ggplot(rdf1, aes(x=rdata1)) +
  geom_histogram(fill="blue", color="black", bins=9) +
  labs(x="Value", y="Frequency", title="Histogram of 10 Samples From the Binomial Distribution Frequencies") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplot(rdf2, aes(x=rdata2)) +
  geom_histogram(fill="blue", color="black", bins=9) +
  labs(x="Value", y="Frequency", title="Histogram of 100 Samples From the Binomial Distribution Frequencies") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplot(rdf3, aes(x=rdata3)) +
  geom_histogram(fill="blue", color="black", bins=9) +
  labs(x="Value", y="Frequency", title="Histogram of 1000 Samples From the Binomial Distribution Frequencies") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
# normal distribution

ndata1 <- rnorm(10, 10, 0.5)
ndf1 <- data.frame(ndata1 = ndata1)

ndata2 <- rnorm(100, 10, 0.5)
ndf2 <- data.frame(ndata2 = ndata2)

ndata3 <- rnorm(1000, 10, 0.5)
ndf3 <- data.frame(ndata3 = ndata3)

ggplot(ndf1, aes(x=ndata1)) +
  geom_histogram(fill="skyblue", color="black", bins=9) +
  labs(x="Value", y="Frequency", title="Histogram of 10 Samples From the Normal Distribution Frequencies") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplot(ndf2, aes(x=ndata2)) +
  geom_histogram(fill="skyblue", color="black", bins=9) +
  labs(x="Value", y="Frequency", title="Histogram of 100 Samples From the Normal Distribution Frequencies") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplot(ndf3, aes(x=ndata3)) +
  geom_histogram(fill="skyblue", color="black", bins=9) +
  labs(x="Value", y="Frequency", title="Histogram of 1000 Samples From the Normal Distribution Frequencies") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

We can see from both the normal and binomial distributions that as sample size increases, the distribution shape becomes more bell-shaped. 

For the binomial distribution, increasing the sample size will result in a more bell-shaped distribution. Additionally, the probability of success (p) in the binomial number generator is 0.5, which would also help give the distribution it's traditional bell-shaped distribution centered in the middle of the graph.

For the normal distribution, we see that increasing the sample size also created a more bell-shaped distribution. As more samples are taken, the shape of the histogram reflects the true shape of the normal distribution with the specified arguments applied.

## Class Survey Data

```{r}
class_data <- read.csv("MSDS_survey.csv")

ggplot(class_data, aes(x=RAM..in.GB.)) +
  geom_histogram(fill="Red", color="black") +
  labs(x="RAM", y="Count", title="Histogram of RAM Storage Distribution") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
  
ggplot(class_data, aes(x=CPU.Number.of.Cores..int.)) +
  geom_histogram(fill="light grey", color="black") +
  labs(x="Number of Cores", y="Count", title="Histogram of Number of Cores") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

Some variables in the data set were not quantitative, continuous variables. Therefore, the distributions of those particular variables could not be shown by a histogram. Examples of these variables are the Github username variable and the operating system variable, among others.